% Statement of Qualifications — Brandon Miner
% Tailored: Administrative Services Analyst (Records Retention, Forms Management, Property Control)

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{microtype}

\definecolor{ruleclr}{gray}{0.4}
\definecolor{headingclr}{gray}{0.15}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small\color{ruleclr}\thepage}

\titleformat{\section}
  {\large\bfseries\color{headingclr}}
  {}
  {0em}
  {}
  [\vspace{2pt}{\color{ruleclr}\hrule height 0.5pt}\vspace{4pt}]

\titlespacing*{\section}{0pt}{18pt}{6pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{7pt}
\linespread{1.15}

\begin{document}

\begin{center}
  {\LARGE\bfseries Brandon Miner}\\[4pt]
  San Francisco, CA \quad\textbullet\quad
  \href{mailto:brandonm333@outlook.com}{brandonm333@outlook.com} \quad\textbullet\quad
  \href{https://www.linkedin.com/in/brandon-miner-3x3}{linkedin.com/in/brandon-miner-3x3} \quad\textbullet\quad
  \href{https://github.com/Brandonminer333}{github.com/Brandonminer333}
\end{center}

\vspace{6pt}
\noindent\textbf{Position applied for:} Administrative Services Analyst
\hfill\textbf{Date:} 07/03/2026

\vspace{8pt}
{\color{ruleclr}\hrule height 0.8pt}
\vspace{12pt}

\section{Introduction}

I am applying for the Administrative Services Analyst position serving as the District's Records Retention and Forms
Management Coordinator, Administrative Property Control Liaison, and lead for administration-related procurement
and the recycle program.
My background combines analytical work, policy-aware record handling, and operational coordination in public-sector
and nonprofit settings.
At the San Diego County Taxpayers Association, I led a team of four analysts standardizing heterogeneous public
records into unified, auditable datasets and delivering findings to county officials.
At the ACLU of Northern California, I manage high-volume sensitive records under strict retention and access constraints,
design standardized intake workflows, and produce audit-ready documentation for legal and advocacy staff.
I hold an M.S. in Data Science and Artificial Intelligence from the University of San Francisco (2026) and a B.S. in
Statistics with Emphasis in Data Science from San Diego State University (2025).
I am prepared to perform the analytical and coordination duties this role requires under the supervision of the
Facility Operations Branch Manager.

\section{Qualification 1 --- Records Retention Policies and Analytical Record Management}

This position requires analytical work supporting retention policies and reliable management of District records.
While my prior titles have been in data science rather than records administration, the substance of my work has
repeatedly centered on organizing, retaining, and governing large record sets according to policy constraints.

At the ACLU of Northern California, I process 600+ sensitive records per month through a standardized intake and
transformation pipeline. Each record moves through defined stages with consistent metadata, structured outputs, and
documentation suitable for audit and review. Partners operate under strict rules about where records may be stored,
who may access them, and how long they remain usable for casework. I designed the system to keep sensitive materials
on approved infrastructure, maintain traceable processing history, and deliver outputs that investigators and legal
staff can rely on without engineering support.

At the San Diego County Taxpayers Association, I built a data standardization pipeline that unified messy public wage
and program records from multiple sources into a single schema. That work required identifying which fields were
authoritative, resolving duplicate and conflicting entries, and documenting assumptions so findings presented to
county officials were defensible.

These experiences translate directly to records retention coordination: applying policy rules consistently,
maintaining organized inventories of what exists and where, and supporting management with clear analysis when
retention or disposition decisions require structured review.

\section{Qualification 2 --- Forms Management and Standardized Administrative Processes}

The Analyst serves as the District's Forms Management Coordinator, ensuring forms and related administrative
processes are consistent, usable, and aligned with operational needs.
I have applied this same discipline in roles where poorly standardized inputs created downstream confusion for
non-technical users.

At the ACLU, I translated investigator workflows into structured data requirements and built a self-service
interface that guides users through consistent steps each time they submit or review material. Rather than relying
on ad hoc email attachments or one-off spreadsheets, the platform enforces a repeatable process: defined inputs,
predictable outputs, and clear handoffs between intake, processing, and review.

At the San Diego County Taxpayers Association, I standardized entity names, job titles, and compensation fields
across heterogeneous public records so analysts and stakeholders could compare records reliably. That work is
directly analogous to forms management: identifying the fields that matter, eliminating ambiguity, and making
administrative data easy for staff to complete and interpret correctly.

I am comfortable reviewing existing processes, recommending improvements, documenting standards, and working with
staff who need practical guidance rather than technical jargon. I would bring the same attention to clarity and
consistency to District forms and related administrative workflows.

\section{Qualification 3 --- Property Control, Asset Tracking, and Operational Accountability}

As Administrative Property Control Liaison, the incumbent supports analytical work in asset control and helps maintain
accountability for District property. My experience includes systematic tracking of resources, artifacts, and
operational assets across distributed environments.

In project and professional work, I have maintained structured inventories of data artifacts, processing outputs,
and deployment resources across local storage, cloud buckets, and application environments. For example, in a
production quiz platform I designed a multi-tier resolver so generated artifacts persisted across restarts and
remained retrievable for reuse, with durable storage in Google Cloud Storage and clear separation between transient
and retained assets. At the ACLU, I track batch processing status, hardware deployment constraints, and the
lifecycle of records from intake through final output.

At the San Diego County Taxpayers Association, I coordinated analytical deliverables across a four-person team,
assigning ownership, monitoring progress, and ensuring completed work was documented and ready for stakeholder use.
That coordination required the same habits asset control depends on: knowing what exists, who is responsible for it,
and when it requires update, review, or retirement.

I would apply this systematic approach to property control liaison duties, supporting accurate tracking, timely
reporting, and practical guidance for staff responsible for District assets.

\section{Qualification 4 --- Procurement Support and Administrative Program Coordination}

The position includes responsibility for administration-related procurement and the District's recycle program.
I have not held a dedicated procurement title, but I have supported administrative program delivery through planning,
resource coordination, and operational follow-through in public-facing organizations.

At the San Diego County Taxpayers Association, I led team workflows from scoping through delivery, balancing competing
priorities across multiple analytical products and ensuring completed work met reporting deadlines for county stakeholders.
At the ACLU, I work independently on end-to-end deliverables while coordinating with legal, advocacy, and operations
colleagues whose approval and input determine whether a system can be adopted.

These roles required documenting requirements before committing resources, communicating status to supervisors,
and maintaining programs that depend on regular attention rather than one-time setup. That is the same operational
mindset procurement and recycle program administration require: clear specifications, reliable follow-up, and
consistent service to internal customers.

I am prepared to learn District-specific procurement and recycling procedures quickly, apply strong organizational
habits, and support the Facility Operations Branch Manager with accurate analysis and dependable coordination.

\section{Qualification 5 --- Analytical Support, Communication, and Public-Sector Service}

Across my roles, analytical work has been inseparable from clear communication and service to non-technical stakeholders.
At the San Diego County Taxpayers Association, I presented workforce and homelessness program findings to county
officials and contributed to public reporting used in policy discussions. At the ACLU, I provide ongoing guidance
to investigators and advocacy staff, explaining what processed records show and what limitations apply.

My training in statistics and data science supports the analytical component of this position: organizing information,
identifying patterns, summarizing findings for management, and recommending practical next steps. I am equally
comfortable working independently on assigned coordinator responsibilities and collaborating with branch staff,
other departments, and external partners when the District's administrative programs require coordinated action.

I am motivated by work that keeps public organizations organized, compliant, and effective behind the scenes.
The Administrative Services Analyst role offers the opportunity to apply my analytical and process-oriented background
to records retention, forms management, property control, procurement, and recycling programs that support the
District's broader mission.

\section{Additional Qualifications}

\begin{itemize}[leftmargin=1.5em, itemsep=3pt, topsep=4pt]
  \item \textbf{Education:} M.S., Data Science and Artificial Intelligence, University of San Francisco (2026);
        B.S., Statistics with Emphasis in Data Science, Minor in Mathematics, San Diego State University (2025)
  \item \textbf{Relevant Experience:} record standardization, audit-ready documentation, workflow design,
        policy-constrained data handling, team coordination, stakeholder reporting
  \item \textbf{Tools:} Python, SQL, Excel-compatible reporting workflows, database-backed record systems,
        cloud and local file storage management, documentation and dashboard tools
  \item \textbf{Work Style:} detail-oriented, process-driven, independent execution with supervisory check-ins,
        clear written and verbal communication with non-technical staff
\end{itemize}

\vspace{16pt}
{\color{ruleclr}\hrule height 0.5pt}
\vspace{10pt}

\noindent I welcome the opportunity to discuss how my experience with standardized records, policy-aware workflows,
and analytical support for public organizations can contribute to the District's administrative operations.
Thank you for your consideration.

\vspace{24pt}
\noindent\textbf{Brandon Miner}\\
\href{mailto:brandonm333@outlook.com}{brandonm333@outlook.com}

\end{document}
